Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-10-01 paper.tex
Updated Paper
Work in progress.

    \subsection{Proposed Solution}
        % It is important to do a literature review for the following papers, there are 
        % other works that tackle similar problems or use it as a strategy. - M 
        In this article, we test various strategies to generate a new population to
        replace individuals that have already died (or were discarded) due to their
        aptitude, as happens in the life cycle. We previously used to generate a new
        random set of solutions, with the cost of losing all evolution knowledge. The
        strategy we describe in this paper uses elites to take advantage of the
        % Where are the elites explained? - M
        historical evolution, especially the best individuals, where we look for the
        offspring of the elite set to be somewhat close to them. We use the golden
        ratio to compute the distance between new individuals in the population, making
        an improved distribution. % Why is better? Explain. - M

        We propose one promising alternative to restart the population, to solve
        extinction caused by nature's pressure in the Life Cycle algorithm: the
        projection of the historically best-found candidate solutions (Elite) towards
        % Move the explanation of Elite to where we use the term for the first time - M
        the best-found candidate solution (Champion). This article proposes some
        strategies to carry out this operation, where the presented distribution
        strategy obtained the best results. % All this goes before they are mentioned. - M

@@

        This strategy is how we can calculate the projection of the historically
        best-found candidate solutions (Elite) towards the best-found candidate
        % You can use Elite now, we all now what it is. - M
        solution (Champion). To illustrate this concept we include
        Figure~\ref{fig.elite_projection}, placing the Elite solution on the far right
        and the Champion solution on the left corner, where a higher number of new
        solutions will be closer to the Champion.

>>>>

    \subsection{Proposed Solution}
        % It is important to do a literature review for the following papers, there are 
        % other works that tackle similar problems or use it as a strategy. - M 
        In this article, we test various strategies to generate a new population to
        replace individuals that have already died (or were discarded) due to their
        aptitude, as happens in the life cycle. We previously used to generate a new
        random set of solutions, with the cost of losing all evolution knowledge.

        This article proposes some strategies to carry out this operation,
        where the presented distribution strategy obtained the best results. We
        propose one promising alternative to restart the population, to solve
        extinction caused by nature's pressure in the Life Cycle algorithm: the
        projection of the historically best-found candidate solutions (Elite)
        towards the best-found candidate solution (Champion).

        The strategy we describe in this paper use an elite set, that includes
        the historically best-found candidate solutions to take
        advantage of the historical evolution. Our goal is for the offspring to
        be somewhat close to the best individuals of the Elite.
        We use the golden ratio to compute the distance between new individuals in the population, making
        an improved distribution. % Why is better? Explain. - M

@@

        This strategy is how we can calculate the projection of the
        historically Elite towards the Champion solution. To illustrate this
        concept, we include Figure~\ref{fig.elite_projection}, placing the
        Elite solution on the far right and the Champion solution on the left
        corner. We can observe the higher amount of new solutions progressively
        closer to the Champion.
